### 2024-08-11 doc/Thesis/chapter/050-results-material.tex
nearly finish with todos from todo.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Properties of the Produced Layers}
\label{sec:res-mat}
%\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC AQUEOUS
As already indicated in the experimental section the aqueous recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
The aqueous solution started out as opaque slurry in contrast to the buthanolic recipe which became opaque only after degrading. 
%\td{Die wässrige Lösung hatte direkt nach erzeugung viskose und undurchsichtige Eigenschaften - im Gegensatz zu der anderen Lösung, welche erst nach Stunden von klar auf undurchsichtig umschwenkte.}
%The solution was opaque from the beginning and 
Furthermore, the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the measured resistance through the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, 
there was no significant improvement and the \gls{sem} images (see figure~\ref{fig:sem-old}) 
showed highly inhomogeneous deposition, with deposited  areas next to other areas where the conductive substrate (ITO or FTO) can be clearly seen  uncoated.
%reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aqueous recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aqueous recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/071_fto_old_2x.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of \gls{zro}:
		(a) \gls{zro} produces by 2 layers aqueous solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}
\enlargethispage{-\baselineskip}

The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimized, led to improved results (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible cracks spread across the surface could depict such pin holes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}

@@

%%%%%%%%% CROSS SECTION
Figure~\ref{fig:sem-cs1} shows the cross-section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe) can be observed.
Measuring the cross section on steel was not as straight forward. 
%because the ductility of steel prevents fractures of the substrate. 
%Resorting to 
Scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure~\ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray Diffractogram of \ch{ZrO2}}
%\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow; below), \gls{zro} (blue; above), $\alpha$-Fe (green; wide; idealized) and cubic-\gls{zro} (purple; narrow; idealized)\cite{gkatz1971xray} }%\td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

@@

In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmittance spectra of \gls{zro} layers on glass slides can be seen. 
Each sample had different numbers of coated layers. 
The incident angle was \ang{0} for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
This trend can also be observed in figure~\ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements. 
%
Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of \ang{45}. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Current Voltage Curves of \ch{ZrO2} Layers} 
%\todo{of what?}
\begin{figure}
    \centering
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-optimization of Coating Procedure}
%\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} speed $v_{C}$ (i.e.\ the speed with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} speed, the more uniformly the solution evaporated. 
If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} speed $v_{C}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Properties of Produced Layers}
\label{sec:res-mat}
%\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC AQUEOUS
As already indicated in the experimental section the aqueous recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
The aqueous solution started out as opaque slurry in contrast to the buthanolic recipe which became opaque only after degrading. 
%\td{Die wässrige Lösung hatte direkt nach erzeugung viskose und undurchsichtige Eigenschaften - im Gegensatz zu der anderen Lösung, welche erst nach Stunden von klar auf undurchsichtig umschwenkte.}
%The solution was opaque from the beginning and 
Furthermore, the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the measured resistance through the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two coating layers, 
there was no significant improvement and the \gls{sem} images (see figure~\ref{fig:sem-old}) 
showed highly inhomogeneous deposition, with deposited  areas next to other areas where the conductive substrate (ITO or FTO) can be clearly seen  uncoated.
%reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aqueous recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aqueous recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/071_fto_old_2x.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of \gls{zro}:
		(a) \gls{zro} produced by 2 layers aqueous solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross-section of crack of 5 layers of \gls{zro} on \gls{fto}
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}
\enlargethispage{-\baselineskip}

The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimized, led to improved results (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 coating layers produced from  the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pinhole, a hole in the coating layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible cracks spread across the surface could depict such pinholes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pinholes were electrically observed on similar samples. \todo{where is the evidence?}

@@

%%%%%%%%% CROSS SECTION
Figure~\ref{fig:sem-cs1} shows the cross-section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe) can be observed.
Measuring the cross-section on steel was not as straight forward. 
%because the ductility of steel prevents fractures of the substrate. 
%Resorting to 
Scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure~\ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-Ray Diffractogram of \ch{ZrO2}}
%\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow; below), \gls{zro} (blue; above), $\alpha$-Fe (green; wide; idealized) and cubic-\gls{zro} (purple; narrow; idealized)\cite{gkatz1971xray} }%\td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

@@

In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmittance spectra of \gls{zro} layers on glass slides can be seen. 
Each sample had different numbers of coated layers. 
The incident angle was \ang{0} for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more coating layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is, the more turning points can be identified on the graph, which can be attributed to interference\cite{Dumin1967}.
This trend can also be observed in figure~\ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements. 
%
Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of \ang{45}. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker coating layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Current Voltage Curves of \ch{ZrO2} Layers} 
%\todo{of what?}
\begin{figure}
    \centering
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pinhole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-Optimization of Coating Procedure}
%\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} speed $v_{C}$ (i.e.\ the speed with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} speed, the more uniformly the solution evaporated. 
If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} speed $v_{C}$.
